### 2022-08-07 paper/Chapters/Chapter02.tex
update paper

Surface normal inference is a widely researched topic and can be solved in multiple directions. Traditionally, it can be inferred from a point cloud. There exists many optimization based approaches to pixel-wise calculate surface normal using neighbor information of each point (\cite{optimized-methods}). \cite{Holzer.S} proposed method to use local neighbors with an interest parameter $ p $ and compute the eigenvectors of the corresponding covariance matrix.  These approaches perform well on dense input data based on a well-chosen window size. However, in many practical dataset, like  (\cite{nyu} and \cite{kitti-depth}), the geometry information is provided as depth map. The depth map can be used to convert to point cloud but it is usually very noisy with many missing pixels and holes on dark, shinny or transparent regions. It gives more challenge on neighbor based approaches since no neighbor information exists in many of such areas.

In order to ease this problem, some of the approaches focus on depth map enhancement by estimating missing regions.  \cite{depth-inpainting-distribution} proposed an approach considers the depth distributions of neighboring regions to fill the holes in the depth map. \cite{ncnn} use deep learning based approach for semi-dense depth map inpainting, which mainly utilized normalized convolution proposed by \cite{nconv}. This approach considers a 0-1 mask to distinguish valid and invalid data points. \cite{pncnn} improved this approch by proposing an input confidence estimation network to replace the binary mask with a estimated confidence mask. \cite{depth-enhance-guided} uses normalized convolution for depth map inpainting as well and also use RGB image as the guidance.

On the other hand, some of the approaches use RGB image to estimate depth map or surface normal or use RGB-D image to estimate surface normal. 
\cite{Eigen} proposed a two staged network for depth map prediction based on RGB image, which consider the global features and the local features respectively. \cite{img2depth} also predicts the depth map from image, which employed Residual Network for the feature extraction and further designed a upsampling part with the unpolling layers. 
\cite{binsformer} proposed a method adaptively generate information to predict depth maps based on RGB image. 
\cite{geometry_based_solution} uses RGB-D images to estimate surface normal. It proposed a method to learn discriminative and geometrically informative primitives from RGBD images, which is further used to recover the surface normals of a scene from a single image. 
\cite{GeoNet} uses ResNet (\cite{resnet}) to infer a coarse surface normal based on RGB image, and further refine it with the help of depth map based on the methods based on \cite{geometry_based_solution}. 
\cite{hfm} based on UNet architecture for normal estimation using RGB-D image as input.

However, these approaches are mainly relies on RGB images as input for normal estimation or depth inference and applied for indoor scenarios like bedroom or office, which does not focus on fine details of the surface but only main directions of the regions like direction of floor, walls, seats etc.

>>>>

Surface normal inference is a widely researched topic and can be solved in multiple directions. Traditionally, it can be inferred from a point cloud. There exists many optimization based approaches to pixel-wise calculate surface normal using neighbor information of each point (\cite{optimized-methods}). \cite{Holzer.S} proposed a method to use local neighbors with an interest parameter $ p $ and compute the eigenvectors of the corresponding covariance matrix. These approaches perform well on dense input data based on a well-chosen window size. However, in many practical dataset, like  (\cite{nyu} and \cite{kitti-depth}), the geometry information is provided as a depth map. The depth map can be used to convert to point cloud, but it is usually very noisy with many missing pixels and holes on dark, shiny or transparent regions. It gives more challenge on neighbor based approaches since no neighbor information exists in many of such areas.

In order to ease this problem, some of the approaches focus on depth map enhancement by estimating missing regions. \cite{depth-inpainting-distribution} proposed an approach considers the depth distributions of neighboring regions to fill the holes in the depth map. \cite{ncnn} use deep learning based approach for semi-dense depth map inpainting, which mainly utilized normalized convolution proposed by \cite{nconv}. This approach considers a 0-1 mask to distinguish valid and invalid data points. \cite{pncnn} improved this approach by proposing an input confidence estimation network to replace the binary mask with a estimated confidence mask. \cite{depth-enhance-guided} uses normalized convolution for depth map inpainting as well and also use RGB image as the guidance.

On the other hand, some of the approaches use RGB image to estimate depth map or surface normal or use RGB-D image to estimate surface normal. 
\cite{Eigen} proposed a two staged network for depth map prediction based on RGB image, which consider the global features and the local features respectively. \cite{img2depth} also predicts the depth map from image, which employed Residual Network for the feature extraction and further designed a up-sampling part with the un-polling layers. 
\cite{binsformer} proposed a method adaptively generate information to predict depth maps based on RGB image. 
\cite{geometry_based_solution} uses RGB-D images to estimate surface normal. It proposed a method to learn discriminative and geometrically informative primitives from RGBD images, which is further used to recover the surface normals of a scene from a single image. 
\cite{GeoNet} uses ResNet (\cite{resnet}) to infer a coarse surface normal based on RGB image, and further refine it with the help of depth map based on the methods based on \cite{geometry_based_solution}. 
\cite{hfm} based on UNet architecture for normal estimation using RGB-D image as input.

However, these approaches mainly rely on RGB images as input for normal estimation or depth inference and applied for indoor scenarios like bedroom or office, which does not focus on fine details of the surface but only main directions of the regions like direction of floor, walls, seats, etc.
